Improving phase-matching of FWM with temperature

### 2015-09-20 latex/article.tex
100 factor!

@@

\vspace{18pt}
************************************************************************
\vspace{12pt}

****		è necessario verificare conservazione di energia e momento
\vspace{12pt}

In order to be efficient, the parametric process needs to verify both the conservation of energy and momentum.
$$\omega_1 + \omega_2 = \omega_3 + \omega_4$$
$$\Delta k = \beta_3 + \beta_4 - \beta_1 - \beta_2$$
****
$$\Omega_S = \omega_1 + \omega_3 = \omega_4 - \omega_1$$
where we assume $\omega_3 < \omega_4$.
$$\Omega_S = |\omega_P - \omega_I| = |\omega_S - \omega_P|$$

We can define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=.75\textwidth]{delta_example.png}
	\caption{Example of $L_{coh}$ at $T_H$ fixed.}
	\label{fig_peaks}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{ex_pos.png}
		\caption{Example of peaks vs $T_H$.}
		\label{fig_example_position}
	\end{subfigure}\hspace{.05\textwidth}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{ex_bw.png}
		\caption{Example of bandwidth vs $T_H$.}
		\label{fig_example_bandwidth}
	\end{subfigure}
	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
	\label{fig_examples}
\end{figure}

>>>>

Significant FWM occurs only if the phase match nearly vanishes.
This require the matching of frequencies as well as of the wave vectors.
Thus the phase-matching condition requires a specific choice of input wavelengths and media parameters before FWM can occur with high efficiency.

From the definition of $\phi_-$ and $\phi_+$ we can gather that there are two types of FWM.
The term containing $\phi_-$ correspond to the case in which two photons at frequencies $\omega_1$ and $\omega_2$ are annihilated, while two photons at frequencies $\omega_3$ and $\omega_4$ are created simultaneously.
On the other hand, the term containing $\phi_+$ correspond to the case in which three photons at frequencies $\omega_1$, $\omega_2$ and $\omega_3$ are annihilated, while one photon at frequency $\omega_4$ is created.

Our study focuses on a special condition of the second case, where $\omega_1 = \omega_2 = \omega_P$. The setup is therefore consist of a strong pump of frequency  $\omega_P$ and a signal of frequency  $\omega_3 = \omega_S$, resulting in the creation of the idler wave of frequency $\omega_4 = \omega_I$.
The condition of frequency and phase matching are therefore:
\begin{equation}
\left\{
 	\begin{aligned}
		\omega_I &= 2\omega_P - \omega_S \\
		\Delta k &= 2\beta_P - \beta_S - \beta_I = 0
	\end{aligned}
\right.
\label{eq_f&pmc}
\end{equation} %frequency & phase matching conditions

@@

The solution that we have developed so far is valid only when the pump waves remain largely undepleted.
For a solution that includes pump depletion it is necessary to solve exactly the complete set of four equations, Eqs (\ref{eq_coupled_amplitude_a} - \ref{eq_coupled_amplitude_d}).

We made a further assumption, that is that $\kappa = \Delta k + \gamma(P_1 + P_2) \approx \Delta k$, since $\Delta \gg \gamma(P_1 + P_2)$ almost always.
In order to be efficient, the parametric process needs to verify both the conservation of energy and momentum, as given in Eq. (\ref{eq_f&pmc}).

We can also define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=.75\textwidth]{delta_example.png}
	\caption{Example of $L_{coh}$ at $T_H$ fixed.}
	\label{fig_peaks}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{ex_pos.png}
		\caption{Example of peaks vs $T_H$.}
		\label{fig_example_position}
	\end{subfigure}\hspace{.05\textwidth}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{ex_bw.png}
		\caption{Example of bandwidth vs $T_H$.}
		\label{fig_example_bandwidth}
	\end{subfigure}
	\caption{Examples of peaks position and bandwidth dependence on temperature $T_H$}
	\label{fig_examples}
\end{figure}
